%------------------------
% Resume Template
% Author : Juan R. Ortiz
% Github : https://github.com/juanrortizx
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\flushbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-12pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-8pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeRoleSubheading}[2]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{#1} & \textit{#2} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{center}
  \textbf{\LARGE Juan Ramon Ortiz} \\[4pt]
  \small
  \href{mailto:juanrortiz@proton.me}{juanrortiz@proton.me} ~\textbar~
  909-471-1847 ~\textbar~
  \href{https://github.com/juanrortizx}{github.com/juanrortizx} ~\textbar~
  \href{https://www.linkedin.com/in/juanrortiz}{linkedin.com/in/juanrortiz}
  \normalsize
\end{center}

%----------SUMMARY-----------------
\vspace{0pt}
\section{Summary}
\small{Electrical engineer with 4+ years of industrial automation experience transitioning into embedded systems and IoT software engineering. Hands-on experience in C systems programming, hardware integration, and serial communications. Pursuing an M.S. in Electrical Engineering specializing in Embedded Systems at Cal Poly Pomona.}
\normalsize

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{United Parcel Service (UPS)}{Ontario, California, USA}
    {Corporate PLC Obsolescence Supervisor (Hybrid)}{April 2024 - Present}
    \vspace{-5pt}
    \resumeItemListStart
          \resumeItem{Project Leadership and PLC Programming}{Led the HSLA conversion project to address obsolete controllers running on serial communications. Developed and modified standard PLC programs to resolve compatibility issues. Created a Vijeo Designer HMI program for legacy HMIS5T Magelis Panels to ensure compatibility with Studio 5000.}
          \resumeItem{Legacy Equipment Upgrades}{Upgraded 200+ 1768-L45 controllers to CompactLogix 5069-L320ER nationwide, addressing PLC obsolescence and eliminating unsupported equipment that posed security risks.}
          \resumeItem{Escalation and Technical Support}{Provide fourth-level escalation support for discontinued PLC platforms, resolving ladder logic, I/O, and communications failures through remote and onsite troubleshooting.}
      \resumeItemListEnd

    \resumeRoleSubheading
      {Automation Engineering Specialist (Promoted Internally)}{October 2021 - April 2024}
    \resumeItemListStart
      \resumeItem{Network Troubleshooting}{Led the remapping of the automated network to ensure reliable connectivity by redrawing the ring network in AutoCAD Electrical.}
      \resumeItem{Sensor Integration}{Integrated jam detection sensors into conveyor systems by wiring directly to existing I/O modules, achieving real-time fault detection without modifying PLC logic.}
    \resumeItemListEnd
        
    \resumeRoleSubheading
      {Control Room PT Supervisor (Promoted Internally)}{July 2021 - October 2021}
    \resumeItemListStart
      \resumeItem{Operations Support}{Monitored HMIs to identify fault trends and facilitated troubleshooting between operations, mechanics, and technicians.}
    \resumeItemListEnd

    \resumeRoleSubheading
      {Operations Hub PT Lead (Promoted Internally)}{July 2020 - July 2021}
    \resumeItemListStart
      \resumeItem{Team Leadership}{Led high-volume hub operations, managing staffing, safety communication, and daily execution.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{0pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{EMG-Controlled Prosthetic Hand}{Developed embedded control software on a Teensy 4.1 to drive a robotic prosthetic hand using electromyography signals. Implemented a second-order Chebyshev filter in C for noise reduction, and designed a matrix-based finger position controller with per-finger state tracking. Collaborated on hardware signal conditioning circuit for EMG capture. Tech: C, Teensy 4.1, Arduino IDE, Signal Processing, EMG Sensing}
\vspace{2pt}
%\resumeSubItem{Automated PLC Firmware Upgrade Tool}{Built a Python/C\# tool interfacing with the ControlFlash+ API and Logix Designer SDK to automate firmware flashing and disaster recovery across multiple PLC controllers, reducing process time by 70\%. Tech: Python, C\#, Logix Designer SDK, ControlFlash+ API}
\resumeSubItem{TCP Industrial Logging Tool}{Built a Python CLI tool that connects via TCP to Linux-based industrial control servers, querying and logging system and controls data by target IP. Tech: Python, TCP/IP, Sockets, PowerShell, Linux}
\vspace{2pt}
\resumeSubItem{Minimal OS Memory Optimization}{Reduced a Windows 11 VM to 816MB idle RAM on QEMU/KVM by auditing and disabling kernel services, implementing process lifecycle management via native Win32 API and Rust utilities. Tech: C++, Rust, Win32 API, PowerShell, QEMU/KVM}
\vspace{2pt}
\resumeSubItem{Image Segmentation via DCT Feature Extraction}{Implemented a Bayesian MAP classifier in MATLAB to segment foreground and background in images using 8x8 block DCT features, zig-zag scanning, and class-conditional probability estimation. Tech: MATLAB, Signal Processing, Statistical Classification}
\resumeSubHeadingListEnd

%-----------SKILLS-----------------
\vspace{0pt}
\section{Skills Summary}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}l}
  \textbf{Languages:} & C, Python, PowerShell, Rust, LaTeX \\[2pt]
  \textbf{Embedded \& Systems:} & Win32 API, Memory Optimization, GCC/g++, Cargo \\[2pt]
  \textbf{Dev Environment:} & Linux CLI, QEMU/KVM, SSH, Helix, Zellij, VS Code \\[2pt]
  \textbf{Hardware \& Test:} & Oscilloscopes, DMM, Electrical Soldering and Wire Troubleshooting \\[2pt]
  \textbf{Industry Tools:} & Logix Designer SDK, ControlFlash+ API, Studio 5000 \\[2pt]
  \textbf{Soft Skills:} & Leadership, Project Management, Technical Documentation, Team Collaboration \\ 
\end{tabular*}

%-----------EDUCATION-----------------
\vspace{0pt}
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {California Polytechnic State University}{Pomona, California, USA}
      {Master in Electrical Engineering (M.S.)  Specialization: Embedded Systems}{(In Progress)}
    \vspace{-8pt}
    \resumeItemListStart
      \resumeItem{Courses}{Advanced Robotics, Nanoelectronics (Upcoming)}
    \resumeItemListEnd
    \vspace{-2pt}
    \resumeRoleSubheading
      {Bachelor in Electrical Engineering (B.S.)  Specialization: Control Systems and Robotics}{(Completed)}
    \resumeItemListStart
      \resumeItem{Courses}{Microcontrollers, Signals and Systems, RF Electronics, Advanced Control Systems}
    \resumeItemListEnd
    \resumeSubHeadingListEnd
    \vspace{-8pt}
 \resumeSubHeadingListStart
    \resumeSubheading
      {Riverside City College}{Riverside, California, USA}
      {Associate in Mathematics and Science (A.S.)}{(Completed)}
    \vspace{-5pt}
    \resumeRoleSubheading
      {Associate in Social and Behavioral Studies (A.A.)}{(Completed)}
    \resumeSubHeadingListEnd


% -----------CERTIFICATIONS-----------------
\vspace{-2pt}
\section{Certifications}
\textbf{Rockwell Automation Learning+} --- ControlLogix Fundamentals, Ladder Logic (L1--L4), Maintenance, STL/SFC, Function Block Programming

\end{document}